HBCC - sgACC - FEATURECOUNTS - GRCh38 - CQN

### 2020-04-27 HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd
fix base formula and drop leelvs for mvForwardStepwise

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
#Fit a base model with the following covariates
base_covars <- "Dx"
random_effect <- "Individual_ID"

# Set base formula
base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + ")) %>%
  glue::glue(" + (1|{random_effect})")

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = COVARIATES,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
#Fit a base model with the following covariates
base_covars <- "Dx"

# Set base formula
base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + "))

COVARIATES <- droplevels(COVARIATES)
# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = bar,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```
